|

### 2021-08-22 appendix/appendix.Rmd
commit app

Consider three sets of players: a set of incumbents $ I \ = \ \{ I_1, \ \cdots, \ I_K \}$, a set of challengers $C \ = \ \{ C_1, \ \cdots, \ C_L \}$, and a continuum of $V$ voters.

>>>>

Consider a strategic interaction with three sets of players: a set of incumbents $ I \ = \ \{ I_1, \ \cdots, \ I_K \}$ and a set of challengers $C \ = \ \{ C_1, \ \cdots, \ C_L \}$, and a representative voter $V$.
